Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Some more related work.

\begin{table}
\small
\centering
\begin{tabular}{ l c c c c c c}
App. & resizing barr. & kill & fork & transmit & LoC & data sets\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 & 0 & 4 & 55 & 2\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 & 0 & 0 & 71 & 2\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 & 0 & 3 & 150 & 2\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 & 0 & 0  & 42 & 1\\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 & 0  & 4  & 185 & 2\\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 & 0  & 4  & 196 & 2\\
\rowcolor{Gray3}
octree & 0 / 0 & 1 & 1 & 0 & 213 & 1 \\
\rowcolor{Gray3}
game & 0 / 0 & 1 & 1 & 0 & 308 & 1 \\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia~\cite{...} and Lonestar~\cite{...}
GPU application suites, using global barriers.  We indicate how many of
the original number of barriers are changed to resizing barriers, and
how many variables need to be transmitted.  In all cases all barriers
were converted, except for bc which contains barriers deeper in the call
stack, a case not supported by our prototype. Still, these barriers
could in principle also be converted. The remaining 2 algorithms are
workstealing applications: each required the addition of $\offerfork$
and $\offerkill$ at the start of the main loop, and no variables needed
to be transmitted.  For all these examples the porting to cooperative
kernels was similarly straightforward to the porting illustrated in
\mysec\ref{sec:programmingguidelines} for our running examples, and did
not require reshaping of the original algorithm. Most graph come with 2
different data sets, leading to 13 application/data set pairs in total.

@@

\begin{table}
\small
\centering
\begin{tabular}{ l l l l }
Chip & HD520 & HD5500 & Iris\\
\hline
\# comp. units  & 24 & 24 & 47 \\
Driver   & 20.19.15.4501 & \ADComment{...} & 20.19.15.4463 \\
Host CPU & i3-6100U & \ADComment{...} & i3-5157U \\
\end{tabular}
\caption{The Intel GPU platforms used in our evaluation}
\label{tab:chipstested}
\end{table}

@@

\paragraph{Results}
For each GPU, \mytab\ref{tab:overhead} shows the geometric mean and
maximum slowdown across all applications and data sets, each benchmark
begin run 10 times. For the maximum slowdowns, we indicate which
application and data set was responsible.  The slowdown is below 2 even
in the worst case, and closer to 1 on average. We consider these results
as encouraging, especially since the performance of our prototype could
clearly be improved upon if cooperative scheduling was implemented
directly in the GPU driver.

>>>>

\begin{table}
\small
\centering
\begin{tabular}{ l c c c c }
App. & resizing barriers & kill & fork & transmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 & 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 & 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 & 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 & 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 & 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 & 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 & 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 & 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

\ADComment{It might be good to add a LOC column to \mytab\ref{tab:applications} to indicate how large the original versions of these applicaitons were.}

@@

\ADComment{We need to say something about the number of data sets
  associated with each application, so that we know the total number
  of application/data-set pairs.}

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia~\cite{...} and Lonestar~\cite{...} GPU application suites,
using global barriers.  We indicate how many of the original number of barriers are changed to resizing barriers, and how many variables need to
be transmitted.  In all cases all barriers were converted, except for bc
which contains barriers deeper in the call stack, a case not supported
by our prototype. Still, these barriers could in principle also be
converted.  The remaining 2 algorithms are workstealing applications:
each required the addition of $\offerfork$ and $\offerkill$ at the start
of the main loop, and no variables needed to be transmitted. For all
these examples the porting to cooperative kernels was similarly straightforward to the porting illustrated in \mysec\ref{sec:programmingguidelines} for our running examples, and did not require reshaping of the original algorithm.

@@

\begin{table}
\small
\centering
\begin{tabular}{ l l l l }
Chip & HD520 & HD5500 & Iris\\
\hline
\# compute units  & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
Driver   & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
Host CPU & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
\end{tabular}
\caption{The Intel GPU platforms used in our evaluation}
\label{tab:chipstested}
\end{table}

@@

\ADComment{How many times did we run each benchmark?}

\paragraph{Results}
For each GPU, \mytab\ref{tab:overhead} shows the geometric mean and
maximum slowdown across all applications and data sets.  For the
maximum slowdowns, we indicate which application and data set was
responsible.  The slowdown is below 2 even in the worst case, and
closer to 1 on average. We consider these results as encouraging,
especially since the performance of our prototype could clearly be
improved upon if cooperative scheduling was implemented directly in
the GPU driver.
